---
title: "XXXXXX-XXX Report"
format:
  docx:
    reference-doc: AAGI_Word_Style_Template.docx
    toc: true
    colorlinks: true
    fig-width: 7
    fig-height: 7
execute: 
  echo: false
knitr:
  opts_chunk:
    fig.path: figures/
params:
  uni: CU
bibliography: references.bib
date: "2024-07-05"
---

```{r}
#| include: false
if (params$uni == "CU") {
  Project_Lead = "Curtin University -- Prof Mark Gibberd, Dr Julia Easton, Prof Adam Sparks"
} else if (params$uni == "UA") {
  Project_Lead = "University of Adelaide -- Dr Julian Taylor, Dr Olena Kravchuck"
} else {
  Project_Lead = "University of Queensland -- Prof Scott Chapman, Emeritus Prof Kaye Basford"
}
```

---
author: 
  - "Author: Dr Bunsen Honeydew"
  - "Project Leads: `r Project_Lead`" 
---

```{r}
#| label: load
#| message: false

library(ggplot2)
library(theme.aagi)
library(flextable)
library(dplyr)

# set ggplot2 theme
theme_set(theme_aagi())

# set flextable theme
set_flextable_defaults(
  theme_fun = theme_ft_aagi
)
```

\newpage

# Some Text from George Box

>Science and Statistics
>Aspects of scientific method are discussed: In particular, its representation as a motivated iteration in which, in succession, practice confronts theory, and theory, practice. Rapid progress requires sufficient flexibility to profit from such confrontations, and the ability to devise parsimonious but effective models, to worry selectively about model inadequacies and to employ mathematics skillfully but appropriately. The development of statistical methods at Rothamsted Experimental Station by Sir Ronald Fisher is used to illustrate these themes.

[@Box1976]


# A Table

This {flextable} follows the AAGI style guidelines.

```{r}
#| label: example-table
#| echo: false
#| include: true

ft <- flextable(head(airquality) |> mutate(`Month Name` = "May"))
ft <- theme_ft_aagi(ft)
ft
```

\newpage

# A Histogram

The AAGI theme is automatically applied here as well.

```{r}
#| label: example-histogram

ggplot(diamonds, aes(carat)) + 
  geom_histogram()
```

# References

::: {#refs}
:::
